---
title: "Practical ML course project-Performance Analysis"
author: "Nance"
date: "December 27, 2017"
output:
  html_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## data cleaning: removing index,name, NA and empty columns

```{r, echo=FALSE}
data=read.csv("pml-training.csv")
data=data[,-1]
m=colnames(data[colSums(is.na(data)) == 0])
data=data[,m]
firstrow=data[1,]
emptycols <- colSums(firstrow == "") == nrow(firstrow)
data=data[!emptycols]
data=data[,-1]

```

## build model using random forest with cross validation 

```{r, echo=FALSE}
library(ggplot2)
library(caret)
library(lattice)
intrain=createDataPartition(y=data$classe,p=0.7,list=FALSE)
training=data[intrain,]
testing=data[-intrain,]
rfmodel=train(classe~.,method="rf",trControl=trainControl(method = "cv", number = 10),data=training,ntree=1)
pre=predict(rfmodel,testing)
confusionMatrix(testing$classe,pre)


```



Confusion Matrix and Statistics

          Reference
Prediction    A    B    C    D    E
         A 1667    6    1    0    0
         B    3 1123   11    2    0
         C    0   13 1007    5    1
         D    2    1    5  953    3
         E    0    0    0    4 1078

Overall Statistics
                                          
               Accuracy : 0.9903          
                 95% CI : (0.9875, 0.9927)
    No Information Rate : 0.2841          
    P-Value [Acc > NIR] : < 2.2e-16       
                                          
                  Kappa : 0.9877          
 Mcnemar's Test P-Value : NA              

Statistics by Class:

                     Class: A Class: B Class: C Class: D Class: E
Sensitivity            0.9970   0.9825   0.9834   0.9886   0.9963
Specificity            0.9983   0.9966   0.9961   0.9978   0.9992
Pos Pred Value         0.9958   0.9860   0.9815   0.9886   0.9963
Neg Pred Value         0.9988   0.9958   0.9965   0.9978   0.9992
Prevalence             0.2841   0.1942   0.1740   0.1638   0.1839
Detection Rate         0.2833   0.1908   0.1711   0.1619   0.1832
Detection Prevalence   0.2845   0.1935   0.1743   0.1638   0.1839
Balanced Accuracy      0.9977   0.9896   0.9897   0.9932   0.9977 



## Prediction

```{r, echo=FALSE}
data2=read.csv("pml-testing.csv")
ccc=as.vector(colnames(data))
data3=data2[,colnames(data2)%in%ccc]
ppp=predict(rfmodel,data3)
ppp


```
 
 [1] B A B A A E D B A A B C B A E E A B B B
Levels: A B C D E

## Conclusion

I build the model using random foreset and 10 fold cross validation. I expected the out of sample error is above 80%.